Analysis

### 2021-04-22 R/analysis.Rmd
added calibration to validation

```{r}
library(tidyverse)
library(bper)
library(caret)
library(wru)
```

```{r}
census_api <- "5e4c2b8438222753a7f4753fa78855eca73b9950"

load(file = "data/census_fl.RData")
load(file = "data/census_nc.RData")
load_bperdata(destination = "data", include_blocks = T)

load(file = "data/nc_fl.rda")
load(file = "data/nc_fl_wru.rda")
```

```{r}
source(here("R", "funcs", "classify_and_report.R"))
nc_fl_wru %>% 
  sample_n(1000) %>% 
  classify_and_report(wru = T, wru_geo = "county", test_name = "dk")
```

@@

# Set up test data
sample_vec <- sample(1:nrow(nc_fl), 2e6, replace = FALSE)
nc_fl_tests <- nc_fl[sample_vec, ] 
  # select(-c(birth_year, female))

# Test results holder
tests <- data.frame()

# Full comparisons
wru_all <- nc_fl_wru_tests %>% 
  classify_and_report(wru = T, wru_geo = "block", test_type = "all")
bper_all <- nc_fl_tests %>% 
  classify_and_report(test_type = "all")
tests <- rbind(tests, wru_all, bper_all)

# Place
wru_place <- nc_fl_wru_tests %>% 
  filter(!is.na(place)) %>% 
  classify_and_report(wru = T, wru_geo = "place", test_type = "place")
bper_place <- nc_fl_tests %>% 
  select(-c(block, apartment)) %>% 
  filter(!is.na(place)) %>% 
  classify_and_report(test_type = "place")
tests <- rbind(tests, wru_place, bper_place)

# Zip
bper_zip <- nc_fl_tests %>% 
  select(-c(block, place, apartment)) %>% 
  classify_and_report(test_type = "zip")
tests <- rbind(tests, bper_zip)

# County
wru_county <- nc_fl_wru_tests %>% 
  classify_and_report(wru = T, wru_geo = "county", test_type = "county")
bper_county <- nc_fl_tests %>% 
  select(-c(block, place, zip, apartment)) %>% 
  classify_and_report(test_type = "county")
tests <- rbind(tests, wru_county, bper_county)

# State
bper_state <- nc_fl_tests %>% 
  select(-c(block, place, zip, county, apartment)) %>% 
  classify_and_report(test_type = "state")
tests <- rbind(tests, bper_state)

# No Party
wru_all_np <- nc_fl_wru_tests %>% 
  select(-PID) %>% 
  classify_and_report(wru = T, wru_geo = "block", wru_party = F, test_type = "all_np")
bper_all_np <- nc_fl_tests %>% 
  select(-party) %>% 
  classify_and_report(test_type = "all_np")
tests <- rbind(tests, wru_all_np, bper_all_np)

wru_place_np <- nc_fl_wru_tests %>% 
  select(-PID) %>%
  filter(!is.na(place)) %>% 
  classify_and_report(wru = T, wru_geo = "place", wru_party = F, test_type = "place_np")
bper_place_np <- nc_fl_tests %>% 
  select(-c(party, block, apartment)) %>% 
  filter(!is.na(place)) %>% 
  classify_and_report(test_type = "place_np")
tests <- rbind(tests, wru_place_np, bper_place_np)

bper_zip_np <- nc_fl_tests %>% 
  select(-c(party, block, place, apartment)) %>% 
  classify_and_report(test_type = "zip_np")
tests <- rbind(tests, bper_zip_np)

wru_county_np <- nc_fl_wru_tests %>% 
  select(-PID) %>% 
  classify_and_report(wru = T, wru_geo = "county", wru_party = F, test_type = "county_np")
bper_county_np <- nc_fl_tests %>% 
  select(-c(party, block, place, zip, apartment)) %>% 
  classify_and_report(test_type = "county_np")
tests <- rbind(tests, wru_county_np, bper_county_np)

bper_state_np <- nc_fl_tests %>% 
  select(-c(party, block, place, zip, county, apartment)) %>% 
  classify_and_report(test_type = "state_np")
tests <- rbind(tests, bper_state_np)

save(tests, file = here("data", "tests.rda"))
```

>>>>

```{r Libraries}
library(tidyverse)
library(caret)
library(here)
library(wru)
```

```{r Data Loading}
census_api <- "5e4c2b8438222753a7f4753fa78855eca73b9950"

load(file = "data/census_fl.RData")
load(file = "data/census_nc.RData")
# load_bperdata(destination = "data", include_blocks = T)

load(file = "data/nc_fl.rda")
load(file = "data/nc_fl_wru.rda")

source(here("R", "prep", "clean_race_data.R"))
source(here("R", "funcs", "predict_ethnorace.R"))
source(here("R", "funcs", "classify_and_report.R"))
```

```{r test test}
source(here("R", "funcs", "classify_and_report.R"))
source(here("R", "funcs", "predict_ethnorace.R"))

sample_vec <- sample(1:nrow(nc_fl), 1e5, replace = FALSE)
nc_fl_tests <- nc_fl[sample_vec, ] %>% 
  select(-c(birth_year, female, first_name, apartment))

# Test results holder
t <- data.frame()

# Full comparisons
wru_all <- nc_fl_wru_tests %>% 
  filter(!is.na(block)) %>% 
  classify_and_report(wru = T, wru_geo = "place", test_type = "all")
bper_all <- nc_fl_tests %>% 
  filter(!is.na(block)) %>% 
  classify_and_report(test_type = "all", prior = "last_name")
t <- rbind(t, wru_all, bper_all)

```

```{r wru Models}
source(here("R", "funcs", "classify_and_report.R"))
source(here("R", "funcs", "predict_ethnorace.R"))

sample_vec <- sample(1:nrow(nc_fl), 3e6, replace = FALSE)
nc_fl_wru_tests <- nc_fl_wru[sample_vec, ]

wru_all <- nc_fl_wru_tests %>% 
  filter(!is.na(block)) %>% 
  classify_and_report(wru = T, wru_geo = "block", test_type = "all")
wru_place <- nc_fl_wru_tests %>% 
  filter(!is.na(place)) %>% 
  classify_and_report(wru = T, wru_geo = "place", test_type = "place")
wru_county <- nc_fl_wru_tests %>% 
  filter(!is.na(county)) %>% 
  classify_and_report(wru = T, wru_geo = "county", test_type = "county")
wru_all_np <- nc_fl_wru_tests %>% 
  filter(!is.na(block)) %>% 
  select(-PID) %>% 
  classify_and_report(wru = T, wru_geo = "block", wru_party = F, test_type = "all_np")
wru_place_np <- nc_fl_wru_tests %>% 
  select(-PID) %>%
  filter(!is.na(place)) %>% 
  classify_and_report(wru = T, wru_geo = "place", wru_party = F, test_type = "place_np")
wru_county_np <- nc_fl_wru_tests %>% 
  filter(!is.na(county)) %>% 
  select(-PID) %>% 
  classify_and_report(wru = T, wru_geo = "county", wru_party = F, test_type = "county_np")
```

```{r wru Models}
source(here("R", "funcs", "classify_and_report.R"))
source(here("R", "funcs", "predict_ethnorace.R"))
nc_fl_tests <- nc_fl[sample_vec, ]

tests <- data.frame()

bper_all <- nc_fl_tests %>% 
  filter(block %in% blocks$block) %>% 
  classify_and_report(test_type = "all")
tests <- rbind(tests, wru_all, bper_all)

bper_all_np <- nc_fl_tests %>% 
  filter(block %in% blocks$block) %>% 
  select(-party) %>% 
  classify_and_report(test_type = "all_np")
tests <- rbind(tests, wru_all_np, bper_all_np)

bper_place <- nc_fl_tests %>% 
  select(-c(block, apartment)) %>% 
  filter(place %in% places$place) %>% 
  classify_and_report(test_type = "place")
tests <- rbind(tests, wru_place, bper_place)

bper_county <- nc_fl_tests %>% 
  filter(county %in% counties$county) %>% 
  select(-c(block, place, zip, apartment)) %>% 
  classify_and_report(test_type = "county")
tests <- rbind(tests, wru_county, bper_county)

bper_place_np <- nc_fl_tests %>% 
  select(-c(party, block, apartment)) %>% 
  filter(place %in% places$place) %>% 
  classify_and_report(test_type = "place_np")
tests <- rbind(tests, wru_place_np, bper_place_np)

bper_county_np <- nc_fl_tests %>% 
  filter(county %in% counties$county) %>% 
  select(-c(party, block, place, zip, apartment)) %>% 
  classify_and_report(test_type = "county_np")
tests <- rbind(tests, wru_county_np, bper_county_np)

 bper_zip <- nc_fl_tests %>%
   filter(zip %in% zips$zip) %>%
   select(-c(block, place, apartment)) %>%
   classify_and_report(test_type = "zip")
 tests <- rbind(tests, bper_zip)

 bper_zip_np <- nc_fl_tests %>%
   filter(zip %in% zips$zip) %>%
   select(-c(party, block, place, apartment)) %>%
   classify_and_report(test_type = "zip_np")
 tests <- rbind(tests, bper_zip_np)

 bper_state <- nc_fl_tests %>%
   filter(!is.na(state)) %>%
   select(-c(block, place, zip, county, apartment)) %>%
   classify_and_report(test_type = "state")
 tests <- rbind(tests, bper_state)

 bper_state_np <- nc_fl_tests %>%
   filter(!is.na(state)) %>%
   select(-c(party, block, place, zip, county, apartment)) %>%
   classify_and_report(test_type = "state_np")
 tests <- rbind(tests, bper_state_np)

# save(tests, file = here("data", "tests.rda"))
```

```{r}
a <- nc_fl2 %>% 
  sample_n(1000) %>% 
  select(-block)

a %>%   
  predict_ethnorace()
```

@@

nc_fl_tests <- nc_fl %>% 
  sample_n(2e6) %>% 
  predict_ethnorace() %>%
  mutate(
    race = if_else(race == "aian", "other", race),
    pred_race = if_else(pred_race == "aian", "other", pred_race)
  )
```

```{r}
# Recall investigation

white_wrong <- nc_fl_tests %>% 
  filter(race == "white", pred_race != "white")
black_wrong <- nc_fl_tests %>% 
  filter(race == "black", pred_race != "black")
hispanic_wrong <- nc_fl_tests %>% 
  filter(race == "hispanic", pred_race != "hispanic")
api_wrong <- nc_fl_tests %>% 
  filter(race == "api", pred_race != "api")
other_wrong <- nc_fl_tests %>% 
  filter(race == "other", pred_race != "other")

prop.table(table(white_wrong$pred_race))
nrow(white_wrong)
prop.table(table(black_wrong$pred_race))
nrow(black_wrong)
prop.table(table(hispanic_wrong$pred_race))
nrow(hispanic_wrong)
prop.table(table(api_wrong$pred_race))
nrow(api_wrong)
prop.table(table(other_wrong$pred_race))
nrow(other_wrong)

```

```{r}
# Precision investigation

white_wrong <- nc_fl_tests %>% 
  filter(race != "white", pred_race == "white")
black_wrong <- nc_fl_tests %>% 
  filter(race != "black", pred_race == "black")
hispanic_wrong <- nc_fl_tests %>% 
  filter(race != "hispanic", pred_race == "hispanic")
api_wrong <- nc_fl_tests %>% 
  filter(race != "api", pred_race == "api")
other_wrong <- nc_fl_tests %>% 
  filter(race != "other", pred_race == "other")

prop.table(table(white_wrong$race))
nrow(white_wrong)
prop.table(table(black_wrong$race))
nrow(black_wrong)
prop.table(table(hispanic_wrong$race))
nrow(hispanic_wrong)
prop.table(table(api_wrong$race))
nrow(api_wrong)
prop.table(table(other_wrong$race))
nrow(other_wrong)

```

```{r}
a <- census_geo_api(key = census_api, state = "FL", geo = "county")
```
